FoRTE baseline

### 2019-10-25 analysis/paper/paper.Rmd
Add Figure numbers as comments
...to help keep track in text

```{r , fig.cap = structure_default_cap}
structure_default_cap <- paste(
  htmlfig(),
  "Annual NPP and LAI from ED2 runs",
  "with default parameters",
  "across different configurations."
)
fig("structure-compare-default.png")
```

@@

```{r , fig.cap = structure_default_light_cap}
structure_default_light_cap <- paste(
  htmlfig(),
  "Radiation profiles of cohorts from ED2 runs with",
  "default parameters, across different configurations.",
  "Each point represents a single cohort of the given PFT,",
  "position on the y-axis represents the height of that cohort,",
  "and position on the x-axis represents the relative light level",
  "received by that cohort."
)
fig("default-light-levels.png")
```

@@

```{r param_dist, fig.cap = param_dist_cap}
param_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions from PEcAn trait meta-analysis."
)
fig("param-dist.png")
```

@@

```{r default-median-flux, fig.cap = default_median_flux_cap}
default_median_flux_cap <- paste(
  htmlfig(),
  "Comparing results of ED2 with default parameters and",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
fig("default-median-fluxes.png")
```

```{r default-median-lai , fig.cap = default_median_lai_cap}
default_median_lai_cap <- paste(
  htmlfig(),
  "Comparing results of ED2 PFT-level LAI",
  "with default parameters",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
fig("default-median-lai.png")
```

@@

```{r summary-ts-plot, fig.cap = summary_ts_cap}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "net (NPP) primary productivity and",
  "total leaf area index (LAI),",
  "by model configuration.",
  "The dashed lines indicate the 10th and 90th quantiles of results.",
  "Black dot with error bars is the observed mean and min/max value",
   "(TODO REF)."
)
fig("summary-ts-plot.png")
```

@@

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "ED2 predictions of annual mean NPP and growing-season LAI in 1920, 1950, and 1999",
  "by model type.",
  "Each point indicates a single ensemble run with a different set of parameters.",
  "Solid line is the best-fit generalized additive model (GAM).",
  "Dashed lines indicate the error bounds of present-day observed NPP and LAI.",
  "Text labels match the rows in Figure X below."
)
fig("npp-lai-pairs.png")
```

@@

```{r pft-jitterplot, fig.cap = pft_jitterplot_cap}
pft_jitterplot_cap <- paste(
  htmlfig(),
  "Fraction of total aboveground biomass (AGB)",
  "of each plant functional type (PFT)",
  "predicted by different parameter-configuration combionations",
  "of ED2."
)
fig("pft-jitterplot.png")
```

@@

```{r lai-pft-plot, fig.cap = lai_pft_cap}
lai_pft_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
fig("lai-pft.png")
```

@@

```{r partial-variance-npp, fig.cap = partial_variance_npp_cap}
partial_variance_npp_cap <- paste(
  htmlfig(),
  "Contributions of individual parameters to predicted uncertainty in NPP,",
  "by model type.",
  "Panels on the left are for the \"peak\" NPP period (averaged over 1925-1950),",
  "and on the right are for the end of the simulation (averaged over 1975-1999)",
  "Each panel shows the top 8 parameter values in terms of their variance contribution.",
  "Input parameter distributions are shown in Figure 1.",
  "Note that x-axis scales vary across panels."
)
fig("partial-variance-npp.png")
```

>>>>

```{r structure-compare-default, fig.cap = structure_default_cap}
### Figure 1
structure_default_cap <- paste(
  htmlfig(),
  "Annual NPP and LAI from ED2 runs",
  "with default parameters",
  "across different configurations."
)
fig("structure-compare-default.png")
```

@@

```{r structure-compare-light, fig.cap = structure_default_light_cap}
### Figure 2
structure_default_light_cap <- paste(
  htmlfig(),
  "Radiation profiles of cohorts from ED2 runs with",
  "default parameters, across different configurations.",
  "Each point represents a single cohort of the given PFT,",
  "position on the y-axis represents the height of that cohort,",
  "and position on the x-axis represents the relative light level",
  "received by that cohort."
)
fig("default-light-levels.png")
```

@@

```{r param_dist, fig.cap = param_dist_cap}
### Figure 3
param_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions from PEcAn trait meta-analysis."
)
fig("param-dist.png")
```

@@

```{r default-median-flux, fig.cap = default_median_flux_cap}
### Figure 4
default_median_flux_cap <- paste(
  htmlfig(),
  "Comparing results of ED2 with default parameters and",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
fig("default-median-fluxes.png")
```

```{r default-median-lai , fig.cap = default_median_lai_cap}
### Figure 5
default_median_lai_cap <- paste(
  htmlfig(),
  "Comparing results of ED2 PFT-level LAI",
  "with default parameters",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
fig("default-median-lai.png")
```

@@

```{r summary-ts-plot, fig.cap = summary_ts_cap}
### Figure 6
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "net (NPP) primary productivity and",
  "total leaf area index (LAI),",
  "by model configuration.",
  "The dashed lines indicate the 10th and 90th quantiles of results.",
  "Black dot with error bars is the observed mean and min/max value",
   "(TODO REF)."
)
fig("summary-ts-plot.png")
```

@@

```{r pairs-time, fig.cap = pairs_time_cap}
### Figure 7
pairs_time_cap <- paste(
  htmlfig(),
  "ED2 predictions of annual mean NPP and growing-season LAI in 1920, 1950, and 1999",
  "by model type.",
  "Each point indicates a single ensemble run with a different set of parameters.",
  "Solid line is the best-fit generalized additive model (GAM).",
  "Dashed lines indicate the error bounds of present-day observed NPP and LAI.",
  "Text labels match the rows in Figure X below."
)
fig("npp-lai-pairs.png")
```

@@

```{r pft-jitterplot, fig.cap = pft_jitterplot_cap}
### Figure 8
pft_jitterplot_cap <- paste(
  htmlfig(),
  "Fraction of total aboveground biomass (AGB)",
  "of each plant functional type (PFT)",
  "predicted by different parameter-configuration combionations",
  "of ED2."
)
fig("pft-jitterplot.png")
```

@@

```{r lai-pft-plot, fig.cap = lai_pft_cap}
### Figure 9
lai_pft_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
fig("lai-pft.png")
```

@@

```{r partial-variance-npp, fig.cap = partial_variance_npp_cap}
### Figure 10
partial_variance_npp_cap <- paste(
  htmlfig(),
  "Contributions of individual parameters to predicted uncertainty in NPP,",
  "by model type.",
  "Panels on the left are for the \"peak\" NPP period (averaged over 1925-1950),",
  "and on the right are for the end of the simulation (averaged over 1975-1999)",
  "Each panel shows the top 8 parameter values in terms of their variance contribution.",
  "Input parameter distributions are shown in Figure 1.",
  "Note that x-axis scales vary across panels."
)
fig("partial-variance-npp.png")
```
